---
title: "hydat"
author: "David Tavernini"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{hydat}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## hydat v0.1.0
### About 

The goal of the hydat package is to smoothly and efficiently tidy hydrometric data downloaded from the Government of Canada [Hydat database](https://wateroffice.ec.gc.ca/search/search_e.html?sType=h2oArc). The primary function contained in this package (`hydat_load`) was created to convert the downloaded daily discharge data .csv files to dataframes in "long" format. As time goes by, I'll add other features and functions for quick analysis of data

### Installation

You may install this package through the GitHub repo using `install_github`

```
install.packages("devtools")
devtools::install_github("dtavern/hydat")
```

### Function capabilities

The functions that are available in this package are listed below. Please access the help files through ?function for further detail.

- `hydat_load`: Input .csv file from the hydat database (non-date-data format) and apply various filters to output a new dataframe in long format. 

- `hydat_flooddist`: Input long-format (post-processed by hydat_load) dataframe and output flood frequency table.

### Other objects

- `burpee`: example dataset taken from Burpee Millstream
- `datasymb`: lookup table for measurement codes from the Government of Canada
- `stations`: complete stations list in the HYDAT database

### Examples

Import raw file (using Burpee Millstream as example dataset) using `hydat_load()` omitting estimated values

```{r}
library(hydat)
library(ggplot2)
x <- hydat_load(burpee, omit = "E", na.rm = TRUE)
```

Generate flood frequency distribution usng `hydat_flooddist`

```{r}
xdist <- hydat_flooddist(x)
```

Plot as cumulative distribution

```{r}
ggplot(data = xdist, aes(y = recurrence_int, x = max_q)) +
  geom_line() +
  scale_x_log10()+
  scale_y_log10()
```


